Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-13 main.tex
references and comments
now c and w

\begin{lemma}\label{lem:MLL1->MLS1}
  If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
\end{lemma}

@@

\begin{lemma}\label{lem:shallow}
  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
\end{lemma}

\begin{proof}
  This is a straightforward exercise that we leave to the reader.
\end{proof}

@@

\subsection{Contraction and Weakining}

\subsection{A First Decomposition Theorem}

@@

\subsection{Unification Nets}

\subsection{Translation between Unification Nets and $\FOMLL$}

\subsection{Translation between Unification Nets and Fonets}

>>>>

\begin{lemma}\label{lem:MLL1->MLS1}
  If $\sqn\Gamma$ is rectified and provable in $\FOMLL$ then $\form\Gamma$ is provable in  $\FOMLS$. \todo{check: do we need rectified here?}
\juihsuan{no}
\end{lemma}

@@

\begin{lemma}\label{lem:shallow}
  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
\end{lemma}
\juihsuan{For this, we need the introduction rule of $\fff$ in $\FOMLL$
(consider the $\aiD$ rule). But if we add it, we'll need the
$\mathsf{ai}\downarrow$ rule to have Lemma \ref{lem:MLL1->MLS1}}
\lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
\begin{proof}
  This is a straightforward exercise that we leave to the reader.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contraction and Weakining}

The first observation here is that Lemmas~\ref{lem:MLL1->MLS1}--\ref{lem:MLS1->MLL1} from above also hold for $\FOLK$ and $\FOKS$. We therefore immediately have:

\begin{thm}\label{thm:LK1-KS1}
  For every sequent $\Gamma$, we have that $\sqn\Gamma$ is provable in
  $\FOLK$ if and only if $\form\Gamma$ is provable in $\FOKS$.
\end{thm}

Then Theorem~\ref{thm:KS} is an immediate consequence. Let us now
proceed with providing further lemmas that will be needed for the
other results.

\begin{lemma}
  \label{lem:ac}
  The $\cD$-rule is derivable in $\set{\acD,\me,\mfaD,\mexD,\fequ}$. 
\end{lemma}

\begin{proof}
  \todo{}
\end{proof}

\begin{lemma}
  \label{lem:me}
  The rules $\me,\mfaD,\mexD$ are derivable in $\set{\wlD,\wrD,\cD}$. 
\end{lemma}

\begin{proof}
  \todo{}\lutz{also check for the need of$\fequ$}
\end{proof}

\begin{lemma}
  Let $A$ and $B$ be formulas. Then
  \begin{equation}
    x
  \end{equation}
\end{lemma}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A First Decomposition Theorem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unification Nets}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Translation between Unification Nets and $\FOMLL$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Translation between Unification Nets and Fonets}
